%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Based on:
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper, 10pt]{article} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
%\defaultfontfeatures{Ligatures=TeX}
\setmainfont{EB Garamond} % Main document font

\usepackage{url, parskip, microtype, ragged2e} % Formatting packages

\usepackage[usenames, dvipsnames]{xcolor} % Required for specifying custom colors

\usepackage{hyperref} % Required for adding links and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks, breaklinks, urlcolor=linkcolour, linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0.0in}{0.0in}{0.0in} % Spacing around sections

\usepackage[hmargin=0.5in, vmargin=0.5in]{geometry}

\usepackage[none]{hyphenat}  % disable this to enable hyphenation

\begin{document}

\pagestyle{empty}  % Removes page numbering

\topskip 0pt
\vspace*{\fill}  % vertically center

%----------------------------------------------------------------------------------------
%    NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\centering{\Huge\textsc{Adam Martinez}}

\vspace{-0.5em}

\begin{center}
\href{mailto:adam.paul.martinez@gmail.com}{adam.paul.martinez@gmail.com} \\
(330) 608-5940
\end{center}

%\vspace{0.3em}

%----------------------------------------------------------------------------------------
%    WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\justify

\textsc{Senior Data Science Manager \hfill Jan 2020 - Present} \\
\textsc{PNC Financial Services \hfill Cleveland, OH}
\begin{itemize}
 \item Subject matter expert and strategic advisor to executive leadership for machine learning (ML) application delivery across various lines of business \textemdash\hspace{0.00em} anti-money laundering, retail banking and lending, and corporate and institutional banking.
 \item Trained a team of 7 Machine Learning Engineers in support of an enterprise-wide Center of Excellence.
 \item Designed and delivered a CI process leveraging Jenkins/Artifactory/Conda-pack for data science-related open-source dependency management.
 \item Proposed, designed, and led development of a ``Lightweight'' model delivery framework for rapidly moving ML models from lab to production environments, acting as both Agile product owner and application owner.
 \item Delivered over \$60M in one-time value and \$7M in year-over-year cost savings via product solution design and technical delivery of 12 machine learning models to include Random Forest, XGBoost, HDBSCAN, and ARIMA/SARIMAX models, implemented with scikit-learn, NLTK, Kafka, OpenShift Container Platform, FastAPI, and PySpark on Hadoop.
\end{itemize}

\textsc{Principal Application Developer \hfill Mar 2019 - Dec 2019} \\
\textsc{PNC Financial Services \hfill Brecksville, OH}
\begin{itemize}
 \item Business solution designer for 3 risk modeling teams, supporting end-to-end delivery of over 30 models and a dozen modeling teams.
 \item Technical solution architect for 4 crews, responsible for implementing business solutions.
 \item Advised management on personnel decisions, shaping team culture and employee development.
\end{itemize}

\textsc{Lead Application Developer \hfill May 2017 - Mar 2019} \\
\textsc{PNC Financial Services \hfill Brecksville, OH}
\begin{itemize}
 \item Python technical lead for 4 crews, responsible for technical design and best practices.
 \item Oversaw conversion of project team from waterfall to agile scrum methodology.
% \item Provided wing-level (scrum-of-scrum) technical guidance.
% \item Assisted crews with story grooming, sprint planning, and setting and maintaining standards of technical excellence.
% \item Provided training and education on new/developing technologies for all crews.
 \item Designed and implemented a data pipeline for supporting regulatory reporting requirements with Pandas/Dask/Matplotlib.
\end{itemize}

%\textsc{Senior Application Developer \hfill Mar 2016 - May 2017} \\
 \textsc{Application Developer / Senior Application Developer \hfill May 2015 - May 2017} \\
\textsc{PNC Financial Services \hfill Brecksville, OH}
\begin{itemize}
 \item Led a crew to design and build web- and cluster-based automation tools for CCAR, DFAST, and CECL regulatory modeling efforts.
% \item Designed system architecture and wrote high-level design documents.
% \item Designed and implemented a solution for a back-end job queuing system on a SAS Grid.
 \item Wrote proof-of-concept software for ML classification of financial data with PySpark/Hadoop.
 \item Drove adoption of best practices, including usage of Git and integrations with Jenkins and Ansible to enable CI/CD.
\end{itemize}

%\textsc{Application Developer \hfill May 2015 - Mar 2016} \\
%\textsc{PNC Financial Services \hfill Brecksville, OH}
%\begin{itemize}
% \item Built financial modeling software for credit loss models.
% \item Prototyped low-level design of regulatory summarization and reporting pipeline.
% \item Created Python/Pandas utilities for summary analysis.
%\end{itemize}

\textsc{Operations Sergeant \hfill Apr 2013 - May 2015} \\
\textsc{United States Army Reserve \hfill Joint Base McGuire-Dix-Lakehurst, NJ}
\begin{itemize}
 \item Taught radio operation, small unit tactics, and leadership tactics, techniques, and procedures.
 \item Trained over 300 personnel in both classroom settings and field environments in preparation for overseas mobilization.
 \item Maintained accountability of over \$1M worth of advanced radio and cryptographical equipment.
% \item Created and briefed studies, analyses, and presentations to help leadership make informed decisions, and implemented their solutions.
\end{itemize}

%------------------------------------------------

%\textsc{Adjunct Faculty} \hfill \textsc{The University of Akron, Akron, OH} \\
%\textsc{Aug 2011 - Dec 2012} \\
%\end{tabu} \\
%    Taught college-level mathematics, including precalculus and algebra.
%    Wrote lesson plans, tests, and assigned grades for classes of more than 40 students.
%    Analyzed and summarized research data using a variety of mathematical techniques. \\

%----------------------------------------------------------------------------------------
%    EDUCATION
%----------------------------------------------------------------------------------------

%\section{Education}
\hrulefill

\textsc{Master of Science in Applied Mathematics} \hfill \textsc{Graduated Dec 2011} \\
\textsc{The University of Akron \hfill Akron, OH} \\
Applied Field: Computer Science \\
Thesis: ``A Geometric Tiling Algorithm For Approximating Minimal Covering Sets'' \

%\textsc{Bachelor of Science in Applied Mathematics} \hfill \textsc{Graduated Cum Laude Dec 2009} \\
%\textsc{The University of Akron \hfill Akron, OH} \\
%Minor: Computer Science


%----------------------------------------------------------------------------------------
%    SKILLS AND CERTIFICATIONS
%----------------------------------------------------------------------------------------

%\section{Skills}
%\hrulefill

\textsc{AI and Machine Learning Skills} \\
    Supervised Classification, Regression, and Clustering Models: \\
    Linear/Logistic Regression,
    Time-Series Models,
    Support Vector Machines,
    Ensemble/Boosted Decision Trees,
    Neural Networks.

%\textsc{Mathematical Skills} \\
%    Linear Algebra,
%    Numerical Computation,
%    Partial Differential Equations,
%    Optimization,
%    Combinatorics,
%    Graph Theory,
%    Statistics.
    
\textsc{Computing Skills} \\
    Expert:
        Python,
        Pandas,
        NumPy,
        SciPy,
        scikit-learn,
        Git,
        Certified Azure Administrator Associate. \\
    Intermediate:
        PySpark,
        Tensorflow,
        Hadoop,
        Dask,
        Jenkins,
        Linux,
        Bash,
        Fortran,
        MATLAB,
        \LaTeX. \\
%    Additional Interests:
%        C\#,
%        C,
%        Rust,
%        Go. \\

\vspace*{\fill}

\end{document}
