%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Based on:
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper,11pt]{article} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont{EB Garamond} % Main document font

\usepackage{url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{0pt}{0pt} % Spacing around sections

\usepackage[hmargin=0.5in, vmargin=0.5in]{geometry}

\usepackage[none]{hyphenat}  % disable this to enable hyphenation

\usepackage{tabu}
\newcommand\tabuwidth{\textwidth}  % set width of tabu tables
\newcommand\rcol{275}  % set relative width of right column, left column width is 100

\begin{document}

\pagestyle{empty} % Removes page numbering

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\centering{\Huge\textsc{Adam Martinez}} % Your name

\begin{center}
\href{mailto:adam.paul.martinez@gmail.com}{adam.paul.martinez@gmail.com} \\
(330) 608-5940
\end{center}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{center}
\begin{tabu} to \tabuwidth {X [r, 100] X [j, \rcol]}

\textsc{Lead Application Dev.} & PNC Financial Services, Brecksville, OH \\
\textsc{May 2017 - Present} &
	Oversaw conversion of project team from waterfall to agile scrum methodology.
	Python technical lead for 3 crews (\textasciitilde 24 developers/analysts).
	Provided wing-level (scrum-of-scrum) technical guidance.
	Assisted crews with story grooming, sprint planning, and setting and maintaining standards of technical excellence.
	Provided training and education on new/developing technologies for all crews.\\

\\ %------------------------------------------------

\textsc{Senior Application Dev.} & PNC Financial Services, Brecksville, OH \\
\textsc{Mar 2016 - May 2017} &
	Lead a team of 9 developers to build web-based and system automation tools for a SAS Grid compute cluster.
	Designed system architecture and wrote high-level design documents.
	Wrote proof-of-concept software for classifying financial data using machine learning and PySpark/Hadoop.
	Drove adoption of Git source code management software and software development best practices, including integrations with Jenkins and IBM uDeploy to enable continuous integration and delivery. \\

\\ %------------------------------------------------

\textsc{Application Developer} & PNC Financial Services, Brecksville, OH \\
\textsc{May 2015 - Mar 2016} &
	Built financial modeling software for CCAR and DFAST credit loss models.
	Prototyped low-level design of CCAR and DFAST summarization and reporting pipeline.
	Created Python/Pandas utilities to assist in result analysis. \\

\\ %------------------------------------------------

\textsc{Observer/Coach Trainer} & United States Army Reserve, Joint Base McGuire-Dix-Lakehurst, NJ \\
\textsc{Oct 2014 - May 2015} &
	Trained over 300 personnel in both classroom settings and field environments in preparation for overseas mobilization.
	Taught radio operation, small unit tactics, and leadership tactics, techniques, and procedures.
	Maintained accountability of over \$1,000,000 worth of advanced radio and cryptographical equipment. \\

\\ %------------------------------------------------

\textsc{Operations Sergeant} & United States Army Reserve, Fort George G. Meade, MD \\
\textsc{Apr 2013 - Oct 2014} &
	Planned training operations, processed personnel for training, and collated operational information for over 300 personnel.
	Created and briefed studies, analyses, and presentations to help leadership make informed decisions, and implemented their solutions. \\

\\ %------------------------------------------------

\textsc{Adjunct Faculty} & The University of Akron, Akron, OH \\
\textsc{Aug 2011 - Dec 2012} &
	Taught college-level mathematics, including precalculus and algebra.
	Wrote lesson plans, tests, and assigned grades for classes of more than 40 students.
	Analyzed and summarized research data using both statistical and analytical methods. \\

\end{tabu}
\end{center}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{center}
\begin{tabu} to \tabuwidth {X [r, 100] X [j, \rcol]}

\textsc{Master of Science} & The University of Akron, Akron, OH \\
\textsc{Applied Mathematics} & Applied Field: Computer Science \\
\textsc{Dec 2011} & Thesis: ``A Geometric Tiling Algorithm For Approximating Minimal Covering Sets'' \\

% \\ %------------------------------------------------
% 
% \textsc{Bachelor of Science} & The University of Akron, Akron, OH \\
% \textsc{Applied Mathematics} & Minor: Computer Science \\
% \textsc{Dec 2009} & Graduated Cum Lade \\

\end{tabu}
\end{center}

%----------------------------------------------------------------------------------------
%	SKILLS AND CERTIFICATIONS
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{center}
\begin{tabu} to \tabuwidth {X [r, 100] X [j, \rcol]}

\textsc{Mathematics:} &
	Statistics,
	Optimization,
	Partial Differential Equations,
	Linear Algebra,
	Numerical Computation,
	Combinatorics,
	Graph Theory. \\
\textsc{Computing:} &
	Python (Pandas, NumPy, SciPy, scikit-learn),
	Dask,
	PySpark,
	Git,
	Linux,
	Bash,
	Fortran,
	MATLAB,
	\LaTeX.
	Passing knowledge of C, Rust, Go. \\

\end{tabu}
\end{center}

\end{document}
